Magnetic Inhibition of Convection and the Fundamental Properties of Low--Mass Stars

### 2016-02-09 paper/ms.tex
Updated HR Diagram Figure with Rad Core Masses

\begin{figure*}[t]
    \centering
    \includegraphics[width=0.48\linewidth]{HR_diagram_age_USco.eps} \quad
    \includegraphics[width=0.43\linewidth]{HR_diagram_split_USco.eps}
    \caption{{\bf (a) Hertzsprung-Russell (HR) diagram for Upper Scorpius. The median empirical locus calculated in Section~\ref{sec:data} is shown by the light-gray shaded region. Black points signify HR diagram positions of eclipsing binary members for which masses and radii are known. Over-plotted are predictions from Dartmouth stellar evolution isochrones. Standard (i.e., non-magnetic) isochrones at 5 Myr, 10 Myr, and 15 Myr are shown as short-dashed, dash-dotted, and long-dashed lines, respectively. A single magnetic isochrone at 10 Myr is plotted as a solid yellow line. All models are computed with a solar metallicity. (b) Zoom-in on the high-mass region of the HR diagram. (c) Zoom-in on the low-mass region.}}
    \label{fig:ages}
\end{figure*}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=0.85\linewidth]{USCO5_MR.eps}
    \caption{Mass-radius diagram for stars in eclipsing systems (black points). Model predictions for magnetic and non-magnetic isochrones are the same as in Fig.~\ref{fig:ages}.}
    \label{fig:mrd}
\end{figure}

@@

\section{Discussion}
\label{sec:disc}
An age of {\bf 9 -- 10} Myr gives broad agreement across the HR and mass-radius diagrams. No stellar population in Upper Scorpius {\bf studied here robustly} supports the possibility that the median age of the association is 5 Myr old.\footnote{Ages for B-type members of Upper Scorpius suggest a range of ages from 2 -- 15 Myr depending on whether models account for rotation \citep{Pecaut2012}, providing some support for a younger age.} As noted above, F-type stars appear a few million years older than stars of other spectral types. This is concerning and should be explored further, especially considering that potential missing physics in the models would likely conspire to make F-stars older, not younger. Curiously, most F stars in Upper Scorpius are at a stage of evolution where radii increase and subsequently decrease over a period of roughly 4 Myr, eerily similar to the observed age discrepancy (see Fig.\ \ref{fig:bump} and text below for more details).

%While ages for the F stars remain in doubt, an overall age of 10 Myr provides good agreement with median age for B-type stars near the main-sequence turn-off \citep{Pecaut2012}.

@@

\begin{acknowledgements}
The magnetic Dartmouth stellar evolution code was originally developed with support of National Science Foundation (NSF) grant AST-0908345. This work made use of NASA's Astrophysics Data System (ADS) and the VizieR catalogue access tool by CDS in Strasbourg, France. Figures in this manuscript were produced with Gnuplot 5 \citep{Gnuplot5.0}.
\end{acknowledgements}

>>>>

\begin{figure*}[t]
    \centering
    \includegraphics[width=0.48\linewidth]{HR_diagram_age_USco.eps} \quad
    \includegraphics[width=0.43\linewidth]{HR_diagram_split_USco.eps}
    \caption{{\bf (a) Comparison of theoretical Hertzsprung-Russell (HR) diagram predictions to the observational locus of Upper Scorpius. The median empirical locus calculated in Section~\ref{sec:data} is shown by the light gray shaded region. Black points signify HR diagram positions of eclipsing binary members for which masses and radii are known. Over-plotted are predictions from Dartmouth stellar evolution isochrones. Standard (i.e., non-magnetic) isochrones at 5 Myr, 10 Myr, and 15 Myr are shown as short-dashed, dash-dotted, and long-dashed lines, respectively. A single magnetic isochrone at 10 Myr is plotted as a solid yellow line. Values in parentheses along the magnetic isochrone are predicted radiative core mass fractions ($M_{\rm rad.\ core}/M_{\star}$) at the circled points. All models are computed with a solar metallicity. (b) Zoom-in on the high-mass region of the HR diagram. (c) Zoom-in on the low-mass region.}}
    \label{fig:ages}
\end{figure*}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=0.85\linewidth]{USCO5_MR.eps}
    \caption{Mass-radius diagram for stars in eclipsing systems. {\bf Black points are from \citet{Kraus2015} and \citet{Alonso2015}, while gray points are taken from \citet{Lodieu2015} and \citet{David2015b}.} Model predictions for magnetic and non-magnetic isochrones are the same as in Fig.~\ref{fig:ages}.}
    \label{fig:mrd}
\end{figure}

@@

\section{Discussion}
\label{sec:disc}
An age of {\bf 9 -- 10} Myr gives broad agreement across the HR and mass-radius diagrams. No stellar population in Upper Scorpius {\bf studied here robustly} supports the possibility that the median age of the association is 5 Myr old. As noted above, the median age for F-type stars appears to be a few million years older than stars of other spectral types. This {\bf discrepancy} is {\bf perplexing} and should be explored further, especially considering that potential missing physics in the models would likely conspire to make F-stars older, not younger. Curiously, most F stars in Upper Scorpius are at a stage of evolution where radii increase and subsequently decrease over a period of roughly 4 Myr {\bf (e.g., HD 144548 A). The timescale for this process is} similar to the observed age discrepancy (see Fig.\ \ref{fig:bump} and text below for more details) and may be indicative of potential shortcomings in model physics.

{\bf Age discrepancies also exist with two B-type members of Upper Scorpius: \object{$\tau$ Sco} and \object{$\omega$ Sco}. They exhibit ages between 2 and 5 Myr depending on whether rotation is accounted for in stellar evolution models \citep{Pecaut2012}. Those authors show that there are four other B-type stars that have inferred ages consistent with the 10 Myr median age proposed here, if rotation is taken into account. Notably the four stars that appear older are known binary systems while the two seemingly younger stars do not have a detected companion \citep{Pecaut2012}. The presence of two seemingly young B-type stars may be leveraged to suggest there exists a young population of stars with ages around 5 Myr thus supporting the younger age for the low-mass stellar population and thereby doing away with the need for a magnetic field explanation. However, that scenario requires that the low-mass stars form almost exclusively in a later star formation episode than the higher mass population. Although we cannot definitively rule out this scenario, we find it unlikely and maintain that the {\bf median} age for the low-mass stars is too young compared to the rest of the stellar population in the absence of magnetic inhibition of convection.}

@@

\begin{acknowledgements}
Thank you to Alexis Lavail, Eric Mamajek, James Silvester, and Eric Stempels for reading and commenting on an early version of this manuscript. The magnetic Dartmouth stellar evolution code was originally developed with support of National Science Foundation (NSF) grant AST-0908345. This work made use of NASA's Astrophysics Data System (ADS) and the VizieR catalogue access tool by CDS in Strasbourg, France. Figures in this manuscript were produced with Gnuplot 5 \citep{Gnuplot5.0}.
\end{acknowledgements}
